How to improve your relationship with your future self.

### 2016-06-24 workflow.Rmd
Removing comment from top section becasue of problems making the pdf

---
title: How to improve your relationship with your future self.
author:
- name: Jake Bowers
  affiliation: <jwbowers@illinois.edu>,  University of Illinois at Urbana-Champaign, Departments of Political Science and Statistics; Fellow, White House Social and Behavioral Sciences Team. Nothing in this paper reflect the official position of the US Government. Many thanks to Mark Fredrickson, Brian Gaines, Kieran Healy, Kevin Quinn and Cara Wong for direct help on this document and to Mika LaVaque-Manty and Ben Hansen for many useful discussions on this topic. The source code for this document may be freely downloaded and modified from <https://github.com/jwbowers/workflow>.
- name: Maarten Voors
  affiliation: <maarten.voors@wur.nl>, Wageningen University, Development Economics Group. Special thanks, the EGAP Learning Days 2016 participants in Santiago Chile,  to the BITSS team and the Department of Economics and Ted Miguel at UC Berkeley where Maarten was a visiting researcher during spring 2016.
  <!-- Separate the thanks sections from affiliation and integrate? Wasnt sure how to do this here-->
bibliography: references.bib
csl: american-political-science-review.csl
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
    pdf_document:
      keep_tex: true
      number_sections: true
      fig_width: 7
      fig_height: 7
      fig_caption: true
      template: bowersarticletemplate.latex
      pandoc_args: [
      "-M", "secPrefix=\\S",
      "--filter", "/usr/local/bin/pandoc-crossref"
      ]
      md_extensions: +autolink_bare_uris+ascii_identifiers+tex_math_single_backslash
...

@@

```{r include=FALSE, cache=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).
# knitr settings to control how R chunks work.

>>>>

---
title: How to improve your relationship with your future self.
author:
- name: Jake Bowers
  affiliation: <jwbowers@illinois.edu>,  University of Illinois at Urbana-Champaign, Departments of Political Science and Statistics; Fellow, White House Social and Behavioral Sciences Team. Nothing in this paper reflect the official position of the US Government. Many thanks to Mark Fredrickson, Brian Gaines, Kieran Healy, Kevin Quinn and Cara Wong for direct help on this document and to Mika LaVaque-Manty and Ben Hansen for many useful discussions on this topic. The source code for this document may be freely downloaded and modified from <https://github.com/jwbowers/workflow>.
- name: Maarten Voors
  affiliation: <maarten.voors@wur.nl>, Wageningen University, Development Economics Group. Special thanks, the EGAP Learning Days 2016 participants in Santiago Chile,  to the BITSS team and the Department of Economics and Ted Miguel at UC Berkeley where Maarten was a visiting researcher during spring 2016.
bibliography: references.bib
csl: american-political-science-review.csl
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
    pdf_document:
      keep_tex: true
      number_sections: true
      fig_width: 7
      fig_height: 7
      fig_caption: true
      template: bowersarticletemplate.latex
      pandoc_args: [
      "-M", "secPrefix=\\S",
      "--filter", "/usr/local/bin/pandoc-crossref"
      ]
      md_extensions: +autolink_bare_uris+ascii_identifiers+tex_math_single_backslash
...

@@

  <!-- Separate the thanks sections from affiliation and integrate? Wasnt sure how to do this here-->
```{r include=FALSE, cache=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).
# knitr settings to control how R chunks work.
